### 2020-03-02 manuscript.tex
Update manuscript.tex

Based on the findings which rebutted a previous study \cite{EffeVogt15}, we believed that FGC is a social coordinated norm \cite{Makie etc} in the studied countries (Kenya, Mali, Nigeria and Sierra Leon):  an individual behavioral intention is subjected to the normative ritual in their community.  The norm of FGC is synergistic, based on what women think about other women’s likely position in their community (i.e., likelihood of others to cut their daughters) and values they attached to this practice (i.e., beliefs of FGC benefits).  Our findings suggested that a mother’s intention of cutting their daughters was overdetermined by her community’s overall intention to cut daughters and her personal beliefs of FGC benefits more than her own fgc status and FGC prevalence in the community (see daughrer isoplot x and effect plots x)\cf{Can we use some stat to elaborate our argument?}.  The similar coordination also applied to supporting FGC practice in the future.  The coordinated performance could (or would be?) be a result of subjective norm as perceived social pressure to perform such behaviour or expected choice of conduct \cite{Ajze91}. \cfonly{FGC is less a coordination rite than singling group identity and symbolism \cite{ShelWand11, Youn15}} \cf{But what is this coordination based on if not marriageability?  What can we find from the benefits PCAs?}.  \cfonly{Need to add Hayf05}

That mothers’ beliefs in FGC benefits was a strong predictor of mothers' intentions to allow their daughters to undergo FGC was well studied \cite{PashPonn16} (more), yet our findings suggested that community’s overall intention on forgoing the practice was equally strong if not more forceful.  When influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe08} (more, Bicc11).  It could be a social norm implicitly supported by social sanction (i.e., cutting daughter) \cite{Bicchieri06, MackLeJe08} (confirm).  The correlation between women’s beliefs of FGC benefits and group intention of cutting daughters needs further studied to apprehend intentional behaviour and beliefs of normative practice of FGC for the intervention. \cf{Should the last sentence be in recommendation section?}.  While beliefs of FGC benefits was a clear factor associating with women’s intention of cutting their daughters, our findings could not clarify what benefits exactly the women believed?  As proposed that social norm and the behavior it compels cannot be inferred from personal attitude \cit{Mack18} (in rebuttal letter), a further analysis to entangle the FGC beliefs is expected.

Based on our analysis of the benefit index \cf{the 4 countries’ PCA results}, marriageability was only one benefit for FGC, there were multiple factors in influencing women’s decision of cutting their daughters \cite{MackLeJe08}.  It is likely tat marriageability is no longer a strong belief in community where FGC is still common and new norms are insinuated around \cite{EffeVogt15, ShelWand11} (more).  Reasons for FGC practice could go beyond the belief of marriage prospects and extend to peer convention \cite{ShelWand11}.  
In Ethiopia, the majority of women who were aware of the negative reproductive health effects had not stopped the practice highlighted the possible fear of isolation and being alienated from the cultural system where FGC could be seen as a force of social cohesion \cite{YirgKass12}.  In Kenya, woman's decision on whether to implement FGC on their daughters were likely to relate to collective identity within ethnic groups against broader social changes \cite{Achi14, Hayf05}; similarly findings observed in Nigeria \cite{FreyJohn07, KandMwek09}.

Although FGC prevalence was found a main factor predicting daughter’s FGC status \cite{BoylSvec19} \cf{more cites}, we found that overall community intention explained more variance than FGC prevalence on respondents’ intention of cutting daughters cfonly{ show daughter effect plot}:  What their community members will do is likely to determine what a mother intends to do with their daughters’ FGC status. In this case, what people did (descriptive norm?) was less a force than what they will do.  In other words, - descriptive norm (i.e., FGC prevalence) was undermined by subjective norm (community intentional behaviour of . \cf{One confusing finding is that all the three models showed group fgc benefits are robustly and negatively associated with the responses.}.  Norms sustained through communications and evolve through social interactions \cite{FishAjze10, RimaLapi15}.   FGC is conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} which may evolve into various forms of conventional norms, such as peer convention \cite{GrosHayd19 (confirm), ShelWand11} (more)

@@

Our models showed that the four countries were clearly different in intention of cutting their daughters where Sierra Lion with the highest likelihood Nigeria the least when compared to FGC prevalence where Sierra Leon had the highest prevalence, followed by Mali, Nigeria and Kenya; yet their attitudes of supporting FGC practice was not clear despite the factor of FGC prevalence \cr{figure xx and figure xxx}.  Regarding sociodemographic factors, education (community), wealth (individual and community) and job (individual) did not predict women’s intention on cutting their daughters, nor did gender awareness (community).

We found that modernization defined by wealth, education and work \cite{BoylMcMo02, Youn02} and gender/feminist perspectives \cite{BoylSvec19, DalaLawo10, Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} were not obvious than the convention approach and that was similar to the previous conclusion \cite{Hayf05} \cfonly{to confirm}.  Modernization (e.g., education and high socioeconomic status) had no clear impact on the likelihood of FGC, but education plays an important role in the mother's decision not to circumcise her daughter as in Nigeria \cite{KandNwak09}. Our findings also showed that education and wealth (both individual and community level) were clearly correlated with attitudes towards FGC continuation.  While both wealth level and education of community level had a positive association with FGC discontinuation (i.e., the higher the education and wealth level were, the less likely to support FGC practice in the future), individual education had an opposite correlation; the results was compared to what was observe in Sierra Lion where both individual level of educate and wealth were positively associated with support of FGC abandonment \cite{Sagn14}.

While a daughter’s FGC risk was higher if she was in a community with a higher community-level of women’s extra familial opportunities (e.g., education, paid work and marital background) \cite{GrosHayf19}, our findings showed that community level of education was not a clear determinant of daughter’s FGC risk, compare to a previous study showed that community education had not clear effect on the likelihood of daughter’s FGC future, while the individual education did in Kenya \cite, Hayf05}.  Individual education also found a positive correlation in discontinuation of FGC, such as in Egypt \cite{DalaLawo10, VanMeek16}.

Younger women were also more likely to support and implement FGC on their daughters in our findings \cf{figures xx}, similar to

@@

=========
% education:  \cite{DalaLawo10, KandNwak09, PashPonn16, VanMeek1};

Younger women were more likely to support FGC continuity and had higher intention of cutting their daughters as found in Ethiopia \cite{MashMatt09}

@@

— Limitation —
- No FGC types relating to our response variables
- Not controlling for daughter’s age
- Not considering heterogeneity.

>>>>

Based on the findings which rebutted a previous study \cite{EffeVogt15}, we believed that FGC is a social coordinated norm \cite{Makie etc} in the studied countries (Kenya, Mali, Nigeria and Sierra Leon):  an individual behavioral intention is subjected to the normative ritual in their community.  The norm of FGC is synergistic, based on what women think about other women’s likely position in their community (i.e., likelihood of others to cut their daughters) and values they attached to this practice (i.e., beliefs of FGC benefits).  We propose that a mother’s intention of cutting their daughters was overdetermined by her community’s overall intention to cut daughters and her personal beliefs of FGC benefits more than her own fgc status and FGC prevalence in the community (see daughrer isoplot x and effect plots x)\cf{Can we use some stat to elaborate our argument?}.  The similar coordination also applied to supporting FGC practice in the future.  The coordinated performance could (or would be?) be a result of subjective norm as perceived social pressure to perform such behaviour or expected choice of conduct \cite{Ajze91}. \cfonly{FGC is less a coordination rite than singling group identity and symbolism \cite{ShelWand11, Youn15}} \cf{But what is this coordination based on if not marriageability?  What can we find from the benefits PCAs?}.  \cfonly{Need to add Hayf05}

That mothers’ beliefs in FGC benefits was a strong predictor of mothers' intentions to have their daughters to undergo FGC was well studied \cite{PashPonn16} (more), yet our findings suggested that community’s overall intention on forgoing the practice was equally strong if not more forceful.  When influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe08} (more, Bicc11).  It could be a social norm implicitly supported by social sanction (i.e., cutting daughter) \cite{Bicchieri06, MackLeJe08} (confirm).  The correlation between women’s beliefs of FGC benefits and group intention of cutting daughters needs further studied to apprehend intentional behaviour and beliefs of normative practice of FGC for the intervention. \cf{Should the last sentence be in recommendation section?}.

Based on our analysis of the benefit index \cf{the 4 countries’ PCA results}, marriageability was only one benefit for FGC, there were multiple factors in influencing women’s decision of cutting their daughters \cite{MackLeJe08}.  It is likely that marriageability is no longer a strong belief in community where FGC is still common and new norms are insinuated around \cite{EffeVogt15, ShelWand11} (more).  Reasons for FGC practice could go beyond the belief of marriage prospects and extend to peer convention \cite{ShelWand11}.  
In Ethiopia, the majority of women who were aware of the negative reproductive health effects had not stopped the practice highlighted the possible fear of isolation and being alienated from the cultural system where FGC could be seen as a force of social cohesion \cite{YirgKass12}.  In Kenya, woman's decision on whether to implement FGC on their daughters were likely to relate to collective identity within ethnic groups against broader social changes \cite{Achi14, Hayf05}; similarly findings observed in Nigeria \cite{FreyJohn07, KandMwek09}.

Although FGC prevalence was a main factor predicting daughter’s FGC status \cite{BoylSvec19} \cf{more cites}, we found that overall community intention explained more variance than FGC prevalence on respondents’ intention of cutting daughters cfonly{ show daughter effect plot}:  What their community members will do is likely to determine what a mother intends to do with their daughters’ FGC status. In this case, what people did (descriptive norm?) was less a force than what they will do.  In other words, - descriptive norm (i.e., FGC prevalence) was undermined by subjective norm (community intentional behaviour of . \cf{One confusing finding is that all the three models showed group fgc benefits are robustly and negatively associated with the responses.}.  Norms sustained through communications and evolve through social interactions \cite{FishAjze10, RimaLapi15}.   FGC is conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} which may evolve into various forms of conventional norms, such as peer convention \cite{GrosHayd19 (confirm), ShelWand11} (more)

@@

Our models showed that the four countries were clearly different in intention of cutting their daughters with Sierra Lion of the highest likelihood and Nigeria compared to FGC prevalence where Sierra Leon had the highest prevalence, followed by Mali, Nigeria and Kenya; yet their attitudes of supporting FGC practice was not clear despite the factor of FGC prevalence \cr{figure xx and figure xxx}.  Regarding sociodemographic factors, education (community), wealth (individual and community) and job (individual) did not predict women’s intention on cutting their daughters, nor did gender awareness (community). Modernization defined by wealth, education and work \cite{BoylMcMo02, Youn02} and gender/feminist perspectives \cite{BoylSvec19, DalaLawo10, Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} were not obvious than the convention approach and that was similar to the previous conclusion \cite{Hayf05} \cfonly{to confirm}.

Modernization (e.g., education and high socioeconomic status) had no clear impact on the likelihood of FGC, but education plays an important role in the mother's decision not to circumcise her daughter as in Nigeria \cite{KandNwak09}. Our findings also showed that education and wealth (both individual and community level) were clearly correlated with attitudes towards FGC continuation.  While both wealth level and education of community level had a positive association with FGC discontinuation (i.e., the higher the education and wealth level were, the less likely to support FGC practice in the future), individual education had an opposite correlation; the results was compared to what was observe in Sierra Lion where both individual level of educate and wealth were positively associated with support of FGC abandonment \cite{Sagn14}.

While a daughter’s FGC risk was higher if she was in a community with a higher community-level of women’s extra familial opportunities (e.g., education, paid work and marital background) \cite{GrosHayf19}, our findings showed that community level of education was not a clear determinant of daughter’s FGC risk, compare to a previous study showed that community education had not clear effect on the likelihood of daughter’s FGC future, while the individual education did in Kenya \cite, Hayf05}.  Individual education also found a positive correlation in discontinuation of FGC, such as in Egypt \cite{DalaLawo10, VanMeek16}.  Younger women were also more likely to support and implement FGC on their daughters in our findings \cf{figures xx}, as found in Ethiopia \cite{MashMatt09}

@@

———— stop reading —————
=========
% education:  \cite{DalaLawo10, KandNwak09, PashPonn16, VanMeek1};

@@

— Limitation —
While beliefs of FGC benefits was a clear factor associating with women’s intention of cutting their daughters, our findings could not clarify what benefits exactly the women believed?  As proposed that social norm and the behavior it compels cannot be inferred from personal attitude \cit{Mack18} (in rebuttal letter), a further analysis to entangle the FGC beliefs is expected.

- No FGC types relating to our response variables
- Not controlling for daughter’s age
- Not considering heterogeneity.
